### 2017-12-10 readme.rmd
added to last section

When I look at the entirety of the impressive work done by multiple very talented groups on testing Ctenophora-sister and Porifera-sister, I come to the conclusion that at this time we cannot reject either hypothesis. I just don't find the sensitivity to species sampling, gene sampling, model selection, and now character coding conclusive. This is because I think we need a broader perspective of the support landscape to put the interesting results we already have into context. It isn't that I don't think it is impossible to come to a well-supported result if support for a phylogenetic hypothesis is sensitive to any of these factors, I just don't think we understand the sensitivity of this problem well enough to come to strong conclusions at this time.

I also find the interactions between these factors concerning. I think that the rigorously blocked approach that Feuda *et al.* 2017 very exciting and the way of the future. It can provide a clear picture of the support landscape as it depends on different factors and their interactions. We need to expand this approach.

@@

>>>>

When I look at the entirety of the impressive work done by multiple very talented groups on testing Ctenophora-sister and Porifera-sister, I come to the conclusion that at this time we cannot reject either hypothesis. I just don't find the sensitivity to species sampling, gene sampling, model selection, and now character coding conclusive. I also find the interactions between these factors concerning. We need a broader perspective of the support landscape to put the interesting results we already have into context before we can understand the implications of sensitivity for these hypotheses.

GTR+G and CAT-GTR+G are very similar models that were implemented in carefully controlled ways by Feuda *et al.* 2017, yet provide very different results. What will happen when we consider other similar, adjacent models? It isn't surprising when highly different models give different results, but when adding a single set of parameters gives a radically different result we should be skeptical that we have the final word in the problem under either model. The fact that the authors claim that "recoding is effective at reducing lineage-specific compositional heterogeneity", yet still get highly inconsistent results in different recoded analyses is also problematic. It is also interesting to note that authors of Feuda *et al.* declared another set of analyses ([Pisani *et al.* 2015](http://dx.doi.org/10.1073/pnas.1518127112)) to be the [nail in the coffin of Ctenophora sister](https://twitter.com/gwoerhe/status/671636958926499841) even though it did not use the recoding strategy that they now claim to be essential to testing these hypotheses. Such strong claims manufacture controversy where there is none and, in combination with moving goal posts, give the impression that the only consistent criterion they apply for detecting problems with analyses is finding that they support Ctenophora-sister.

I think that the rigorously blocked approach that Feuda *et al.* 2017 very exciting and the way of the future. It can provide a clear picture of the support landscape as it depends on different factors and their interactions. We need to expand this approach.

@@

Porifera may very well be the sister group to all other animals, but declaring them to be sister based on inconsistent and inconclusive results will make it harder to find out if they are. It discourages the very work that still needs to be done to test Porifera-sister and Ctenophora-sister. It also alienates so many people who want to know the answer (and to make progress on other hard phylogenetic problems) because it makes it seem like phylogenetic methods give radically different results from one day to the next.
